\maketitle{}
\section{ Enums as Constants }

When working with Typescript, which if you are using Angular, then you most
definitely are using Typescript \footnote{I look forward to working with
Reason sometime soon for typechecking, but I digress.}. Care must be taken to
look into all the nuances that Typescript can offer.

\section{ In a non Typescript Setting }

In order to define a constant in a non-Typescript setting, we use the const
declaration to define variables:

\begin{lstlisting}
  const UP = "UP";
  const DOWN = "DOWN";
  const LEFT = "LEFT";
  const RIGHT = "RIGHT";
\end{lstlisting}

\subsection{ Enums an Introduction }
Very simply, Enums allow us to define a set of named constants
\footnote{https://www.typescriptlang.org/docs/handbook/enums.html}.

\begin{lstlisting}
  enum PlaneActionTypes {
      Up = "[Plane] Up",
      Down = "[Plane] DOWN",
      Left = "[Plane] LEFT",
      Right = "[Plane] RIGHT",
  }
\end{lstlisting}

\subsection{ Benefit of Enums over Constants }
Enums allow us to organize a collection of related values. Think of them as
a class for values, wherein the value can only be a string , or number.

\subsection{ Current quirk of String Enums }
String Enums, as opposed to number Enums, have to be constant initialized
with a string literal. To clarify, you might want expect the following to work:

\begin{lstlisting}
  cont prefix = '[Button]'
  enum Direction {
      Up = `${prefix} UP`,
      Down = `${prefix} DOWN`,
      Left = `${prefix} LEFT`,
      Right = `${prefix} RIGHT`,
  }
\end{lstlisting}

However, it does not work , because this is not a string literal, i.e. string
only.

\subsection{ Convention as a Result of Quirk }
As a result of quirk, we need a way of specifying that this action is happening
in relation to a specific object. Even though we do have a set using enums,
when identifying the string on it's own, from a state management (dev tool)
perspective, or console perspective, it will be beneficial to have the string
literal, be explicit on it's own. [Screenshot of a redux devtool would great].
Please reference above subsection, "Enums as an Introduction", for how this
translates to code in principle.
