\maketitle{}
\section{ State Directory Structure }

When one begins an Angular project for the first time, it can be increasingly
difficult to manage ngrx/store. State, while it should ideally be tied to a
feature, as the app moves on, might not neccesarily be tied to a specific
feature, or page. In addition, +state by nature, as a single giant object,
is global by nature. Also, it takes up a large portion of any app. It makes
sense to put all state in a single repository, so that state within the app can
be transparent(go into this a bit more). Finally, for testing purposes, state is
a very large chunk of business logic for app, and deserves it's own module for
bundling, and testing purposes.

\subsection{Data Access Folder/File Structure }
State being a way of accessing data, an appropriate name for the folder/file
tree for state makes sense to be called data-access. It will look something
like the following:

\input{./state/data-access/data-access-tree-structure}

Most notably, all of the state related code is contained within a single
folder. By doing so, it solves all of the above three issues:
\begin{enumerate}
  \item State is global, and therefore can now be used by multiple features
  \item We have the ability to run
  ng test --project=px-illustrator-data-access-code-box and it will run code
  specifically for this data-access feature state
  \item By globalizing naming convention, we can streamline naming convention
  of all global files intended towards working towards the same purpose. Namely,
  our data-services, and features.
  \item In addition, it alleviates the potential issue of circular dependencies.
  If, for instance, we have feature folder A, and feature folder B. B might need
  state from A, and A might need feature state from B. By keeping all of our
  state global, it helps us circumvent this circular dependency problem.
\end{enumerate}
