\section{ Data Models }
\maketitle{}

A data model is an abstract model, that organizes different sorts of data,
and how they relate to each other. Interfaces in Typescript, very much so cater
to this cause. Coupling various functionality together is arguably Typescript's
greatest strength. Imagine 40 functions using the same data model, which has
required properties. If we add a single required property, or change/update
a single required property, the compiler will complain on the 40 functions that
now to be updated. This is incredibly valuable. There are many more benefits
which are beyond the scope of this chapter. However, introducing data-models
does introduce an interesting dilemma.

\subsection{Dilemma with interfaces in Typescript}
In any enterprise data heavy app, the majority of interfaces will
be created to be used in unison with data being retrieved from the backend.
In an Angular setting, this means that we will be using a service to make the
request. In addition, we will be feeding the data through the entire ngrx/store
pipiline, for http requests. Effect > Action > Action > Reducer. In addition,
inside of the component that will be consuming this data, we will also need
to use the interface. Not to mention, if we want to tightly couple our unit
tests to our interface. We want to make sure that there aren't any use cases
that we do not test properly. Data types can be unique. We might be missing as a result of data type(array, dictionary, object), some particular use case.
Integrating data type with component as well, is important. Keeping the
following scenarios in mind:
\begin{enumerate}
  \item Data Services
  \item ngrx/store pipeline (Data Access)
  \item Component (Consuming business logic)
  \item Unit Tests
\end{enumerate}

What would be the ideal place for us to place our interfaces?

\subsection{Data Models Directory Structure}
Data Models, are unique, by the fact that they tie everything together. Data
Models also seems like an appropriate name for the folder containing these interfaces. It is important to note that not all interfaces will go into this folder, but rather interfaces related to data being pulled in from backend. In addition, interfaces created as a result of interacting with aforementioned
data.

\input{./typescript/data-models/data-models-tree-structure}

\subsection{Data Mocks}
You will notice that we have also coupled mocks with each interface. These mocks
help with unit tests, and by keeping them with the interface, it eases the
ability to update when an interface is updated as well. It is obviously of less
importance that these be kept to date, as long as general integrity of data
is represented closely. However, as a rule of thumb, actually hooking mocks
directly into interfaces, so that they closely represent interface, is the
easiest way to make sure unit tests cover all use cases.
