\maketitle{}
\section{ Lib File Structure }

When working in a monospace repo, file archticture is very important, as
different parts of an application tend to be abstracted. First let's outline
the different potential parts of an Angular application.
\\
\\
\begin{forest}
  [libs
    [common
      [animations
      ]
      [assets
      ]
      [core
       [auth]
       [guards]
       [pipes]
       [validators]
      ]
      [models
      ]
      [testing
      ]
      [ui
      ]
      [utils
      ]
      [styles
      ]
      [vendor
      ]
    ]
  ]
\end{forest}

\subsection{ Lib File Structure in Detail }

\subsubsection{Animations}
Animations are where any common animations might go. Things such as ripple
effects, ghost elements, etc. Animations are really a whole different science
when it comes to development, and therefore makes sense for them to have their
own folder.

\subsubsection{ Assets }
This is where commonly re-used assets, such as icons, or logos are used.

\subsubsection{ Core }
Any piece of functionality that is re-used the app is used here.

\subsubsection{ Models }
This is where interfaces used across the app are used. This will simply type
annotations across the app. In addition, when using a place to reference the
full capacity of data requests within app, this model will be a life saver.

\subsubsection{ Testing }
All data mocks that are common, can go here as well. Data tends to be re-used
many different times within different parts of apps. So ideally, all mocks
should go here.

\subsubsection{ UI }
All presententational components go here. Some examples of might go into an
example app is a header, footer, loading spinner, or charts.

\subsubsection{ Utils }
Shared services used across different apps. For instance, dates.

\subsubsection{ Styles }
Any shared styles used across app, for instance spacing, media queries etc.

\subsubsection{ Vendor }
The vendor folder is used to customized 3rd party libraries. Some libraries
customized might include Angular Materal.
