\chapter{ Introduction to Rxjs - The Rxjs Airplane}

\section{ What is Reactive Programming}

Rxjs is a library based on the concept of Reactive programming. To re-iterate 
what we mentioned in the chapter on ngrx. A great founding paper discussing 
reactive programming for concurrent programming can be found here. 
\footnote{http://www-sop.inria.fr/members/Gerard.Berry/Papers/Berry-IFIP-89.pdf}

It discusses the benefit of Real Time Progamming a.k.a., reactive programming.
In it, it discusses the two main benefits of Reactive Programming:
\begin{enumerate}
  \item Asynchronous
  \item Detemrinistic
\end{enumerate}

That would be reactive programming in a nutshell. It makes sure, that one 
function happens after another. In addition, by it's definition of being 
a set of pre-made functions, it gives stability around the way we are 
transforming our data in Angular. I always did, and still love what is in my 
opinion the most equally profound and succint quote on Reacting Progamming by 
Andre Statlz: 

\begin{quote}
  \say{Reactive Programming raises the level of abstraction of your code so you
   can focus on the interdependence of events that define the business logic...}
\end{quote} 
\footnote{This quote can be found in his excellent article on why you should 
consider adopting Reactive programming principles in your app 
https://gist.github.com/staltz/868e7e9bc2a7b8c1f754\#why-should-i-consider-adopting-rp}

I.e. Rxjs allows for cookie cutter code, so that after mastering Reactive 
Progamming, you can apply those same operators time and time again.

\section{How Reactive Progamming Allows for Cookie Cutter Code}
Naturally, the next question becomes, well how does Reactive Programming accomplish cookie 
cutter code. For the sake of brevity, let's jump into a synopsis of what Rxjs 
code is. More effectively, let's talk about Rxjs within the context of Angular.

\section{ Rxjs's Importance in Angular }
Rxjs has a pretty big place in Angular. I would say that in your average app, 
I would consider it as one of the big three, alongside Typescript, and Ngrx. 
Even though these are independent libaries, when working on enterprise Angular
applications, I personally come across them on a day to day basis. So, while 
they are independent entities to Angular, I very much so consider them as part 
of the Angular framework. 

\section{ The Rxjs Observable }
The core of Rxjs, is the ability to program reactively using observables. Rxjs 
offers the ability to create observables, as well as manipulate them. In 
particular, there are four scenarios to keep in mind, when it comes to creating
an observable: 
\begin{enumerate}
  \item promise
  \item counter
  \item event
  \item AJAX request
\end{enumerate}

\subsection{ Promise }
Assuming we were using Apollo client to retrieve data from our GraphQL 
requests, rxjs gives us the ability to transfer data we have retrieved from our
backend into an observable: 
\begin{lstlisting}
import { from } from 'rxjs';

// Create an Observable out of a promise
const data = from(fetch('/api/endpoint'));
// Subscribe to begin listening for async result
data.subscribe((data) => {
  console.log(data);
});  
\end{lstlisting}

In the above we are using rxjs \lstinline{from} method to convert the data we
have into an observable. This way, it can be accessed using subscribe. You 
might be wondering what may be the benefit of using an observable over JSON 
data and a promise in this scenario. Well, the benefit would be that if we do 
plan on mutating this data in the near future, then it will be beneficial to 
have data available as an observable. So that when data is mutated, your 
front end component will register the change. In addition, being that other parts 
of our application are using observables(for instance, through the use of 
subject and next, which we will get to soon), then being able to have them all
follow the same cookie cutter logic, is beneficial to our application. 

\subsection{Counter}
\begin{lstlisting}
import { interval } from 'rxjs';

// Create an Observable that will publish a value on an interval
const secondsCounter = interval(1000);
// Subscribe to begin publishing values
secondsCounter.subscribe(n =>
  console.log(`It's been ${n} seconds since subscribing!`));
\end{lstlisting}

\subsection{Event}
\begin{lstlisting}
import { fromEvent } from 'rxjs';

const el = document.getElementById('my-element');

// Create an Observable that will publish mouse movements
const mouseMoves = fromEvent(el, 'mousemove');

// Subscribe to start listening for mouse-move events
const subscription = mouseMoves.subscribe((evt: MouseEvent) => {
  // Log coords of mouse movements
  console.log(`Coords: ${evt.clientX} X ${evt.clientY}`);

  // When the mouse is over the upper-left of the screen,
  // unsubscribe to stop listening for mouse movements
  if (evt.clientX < 40 && evt.clientY < 40) {
    subscription.unsubscribe();
  }
});
\end{lstlisting}

\subsection{AJAX Request}
\begin{lstlisting}
import { ajax } from 'rxjs/ajax';

// Create an Observable that will create an AJAX request
const apiData = ajax('/api/data');
// Subscribe to create the request
apiData.subscribe(res => console.log(res.status, res.response));
\end{lstlisting}

\section{Operators}

\subsection{Sophisticated Manipulation}
Once an observable has been created, Rxjs provides operators to manipulate 
the data contained within an obserable. The following is a great example. Let's
say that we have an observable. In this observable, we have data for user 
settings. Specifically, there are settings for currency preferences that we 
would like. Within our official schema, it looks something like this: 
\begin{lstlisting}
{
  settings {
    currency: {
      ...
    }
  }
}  
\end{lstlisting}

We would like to make sure that when we subscribe to our data store 
across the application, we pull in a specific subset of data. We can map 
our data within our \lstinline{ngrx/store} data selector. 

\begin{lstlisting}[caption=settings.selector.ts]
const getPostsCollection = createSelector(
  getAllPostEntities,
  getAllPostIds,
  (entities: any, ids: any) => ids.map(id => entities[id])
);
\end{lstlisting}

Without having to specify what data that is every time, we can map our data 
to a specific data field. Here we are using the \lstinline{ngrx/entity} 
library, as well as the \lstinline{map} method to create a collection of 
entities. Very sophisticated, and allows us to pull in all the data we need
within the observable. This keeps logic outside of individual 
component, and therefore re-usable.

\subsection{Link Operators Together}
Rxjs also offers the ability to link operators together. For instance, let's 
say within our entity we want to filter out all numbers that are odd. Then 
we want to square that number:

\begin{lstlisting}
import { filter, map } from 'rxjs/operators';

const nums = of(1, 2, 3, 4, 5);

// Create a function that accepts an Observable.
const squareOddVals = pipe(
  filter((n: number) => n % 2 !== 0),
  map(n => n * n)
);

// Create an Observable that will run the filter and map functions
const squareOdd = squareOddVals(nums);

// Subscribe to run the combined functions
squareOdd.subscribe(x => console.log(x));  
\end{lstlisting}

\mybox{You might be wondering why rxjs cals this a pipe?! Well if not 
familiar with already, the concept of a pipe originally comes form Unix. 
It is the ability to pass information from one process to another. For 
instance, if using a the terminal in Unix, something such as the following
ps aux | grep root | pbcopy; would display all processes, grep specifically 
for those tied to root, and then copy that to the clipboard.}

\subsection{No subscribe, No describe}
In case you didn't get that title, it's a unit testing joke. But for real, if 
you do not call a subscribe on your pipe, it will never be called. Consider the
pipe as the function(which under the hood it is), and subscribe effectively
calling the pipe(i.e. calling function). So, if pipe not being called, that 
might be why.

\subsection{Common Operators}
One of the biggest complaints that many have about Rxjs, is that it's an 
overly bloated library. A while back, a man by the name of Andre Saltz who is
very much so responsible for popularizing observables within Javascript, 
created a library called XStream, to focus just on the operators one needs to 
use on a day to day basis. Primarily, because some people were complaining of 
the vast amount of operators they happened to learn. (One can perhaps complain
on the bloat that the rxjs library adds, however, rxjs introduced tree shaking
in verson 5.5)

Ironically, what this did do, is start to create transparency around what 
would be considered a common operator. The Rxjs then went ahead and started 
creating what would be considered common operators. The following are common 
operators listed by the Angular documentation:
  
\begin{center}
  \begin{tabular}{@{} l *4c @{}}
    \toprule
    {\color{red}Area} & Operators \\
    \midrule
    Creation & \texttt{from},\texttt{fromEvent}, \texttt{of}\tabularnewline
    Combination & \texttt{combineLatest}, \texttt{concat}, \texttt{merge},
  \texttt{startWith} , \texttt{withLatestFrom},
  \texttt{zip}\tabularnewline
  Filtering & \texttt{debounceTime}, \texttt{distinctUntilChanged},
  \texttt{filter}, \texttt{take}, \texttt{takeUntil}\tabularnewline
  Transformation & \texttt{bufferTime}, \texttt{concatMap}, \texttt{map},
  \texttt{mergeMap}, \texttt{scan}, \texttt{switchMap}\tabularnewline
  Utility & \texttt{tap}\tabularnewline
  Multicasting & \texttt{share}\tabularnewline
  \end{tabular}
\end{center}  

I like to call these the Rxjs airplane. 

We will get into these at a very high level at a later time within this book. 
It's important to have this table in mind, so that you know the rxjs operators 
to keep an eye out for. 

\section{Subjects}
It's also a worth noting the use of subjects within rxjs, as they get used
quite often. A subject, in addition to being an observable, is also an observer. 
This means that we can use \lstinline{next} to add a value to an observable. 
Depending on type of subject, the relationship with next will change. Three 
subjects come up quite common, and are worth mentioning simply to keep them in 
mind. 

Before we get to the different types of subjects, let's first lighly graze 
what an observer is(,in addition to the observable which we are already 
familiar with). An observer is simply a set of callback function attached 
to an observable: 
\begin{verbatim}
const observer = {
  next: x => console.log('Observer got a next value: ' + x),
  error: err => console.error('Observer got an error: ' + err),
  complete: () => console.log('Observer got a complete notification'),
};  
\end{verbatim}

Based on the type of callback called, that is the value the observable will 
have. So a subject is this observer type, in addition to the observable type 
already familiar with. With this is mind: 

\begin{lstlisting}[caption=using next on our subject]
// RxJS v6+
import { Subject } from 'rxjs';

const sub = new Subject();

sub.next(1);
sub.subscribe(console.log);
sub.next(2); // OUTPUT => 2
sub.subscribe(console.log);
sub.next(3); // OUTPUT => 3,3 (logged from both subscribers)
\end{lstlisting}

In the above code, calling next will call all previous instantiated observables. 
Note the final next, which is logged from both subscribers, whereas the 2nd next, 
having only one subscriber instantiated, only logs one amount.

\subsection{BehaviorSubject}
\lstinline{BehaviorSubject} As opposed to a subject, allows you to supply an 
initial value. It can be useful when creating something such as a re-usable 
component, and want to supply an initial value. In addition, unit testing, 
and want to circumvent the extra code need to use next, when mocking values. 
\begin{lstlisting}
// RxJS v6+
import { BehaviorSubject } from 'rxjs';

const subject = new BehaviorSubject(123);

// two new subscribers will get initial value => output: 123, 123
subject.subscribe(console.log);
subject.subscribe(console.log);

// two subscribers will get new value => output: 456, 456
subject.next(456);

// new subscriber will get latest value (456) => output: 456
subject.subscribe(console.log);

// all three subscribers will get new value => output: 789, 789, 789
subject.next(789);

// output: 123, 123, 456, 456, 456, 789, 789, 789  
\end{lstlisting}

\subsection{ReplaySubject}
\lstinline{ReplaySubject}, in addition to allowing an initial value, will also 
store the old values. 
\begin{lstlisting}
// RxJS v6+
import { ReplaySubject } from 'rxjs';

const sub = new ReplaySubject(3);

sub.next(1);
sub.next(2);
sub.subscribe(console.log); // OUTPUT => 1,2
sub.next(3); // OUTPUT => 3
sub.next(4); // OUTPUT => 4
sub.subscribe(console.log); // OUTPUT => 2,3,4 (log of last 3 values from new subscriber)
sub.next(5); // OUTPUT => 5,5 (log from both subscribers)  
\end{lstlisting}

In the above code, we have given our \lstinline{ReplaySubject} a buffer size of
3. Therefore, every next we have, before instantiating another subscribe, will 
introduce buffer size of 3. This can be useful for instance, when we are using something 
such as a timeline, or a table of contents, need to access to an observable, and want to 
keep track of all previous selections of user. 

\section{Naming Conventions for Observables}
Hands down, my favorite naming convention in an Angular application is the use of a 
dollar sign \lstinline{$} as an indicator of an observable. Observables started 
becoming popular before the use of Typescript. While Typescript/rxjs does have 
the type annotation of \lstinline{<Observable>} to indicate an observable, I still
approve of the trailing \lstinline{$} to indicate an observable. 

\begin{lstlisting}[caption=Observable Naming Convention]
import { Component } from '@angular/core';
import { Observable } from 'rxjs';

@Component({
  selector: 'app-stopwatch',
  templateUrl: './stopwatch.component.html'
})
export class StopwatchComponent {

  stopwatchValue: number;
  stopwatchValue$: Observable<number>;

  start() {
    this.stopwatchValue$.subscribe(num =>
      this.stopwatchValue = num
    );
  }
}  
\end{lstlisting}

\subsection{Why Dollar sign was chosen as a convention}
You will notice in the above code, for the Observable 
\lstinline{stopwatchValue$}, we add a \lstinline{$} to the end. This is to 
signify that this value is a stream. In many languages such as Java, there is a 
concept called a stream. While similar, there are some distinct difference such 
as: 
\begin{enumerate}
  \item Observables are asynchronous as opposed to Streams, which aren't.
  \item Observables can be subscribed to multiple times. 
  \item Observables are push based, streams are pull based.
\end{enumerate}

Nonetheless, being that streams existed before, and have this sort of naming 
convention, it bled it's way to it's similar cousing the observable. 

\subsection{Benefits of Naming Convention}
The benefits of this naming convention are two-fold: 
\begin{enumerate}
  \item When scanning through code, and looking for observable values
  \item If you want a non-observable value to store observable value, 
  it can simply have no dollar value. This can then be used without a dollar 
  sign, and makes for really transparent code. 
\end{enumerate}

That pretty much wraps the introduction to Rxjs, as I would have liked to 
have been introduced to Rxjs. I hope you like it, because I really wanted 
to help on this one.