\section{ Correlation ID Service }
\maketitle{}

We have addressed in a previous chapter whether, or not when to use state. One
of the more peculiar situations within an Angular application is file upload.
Generally, it is for the following three reasons:
\begin{enumerate}
  \item There is a before, and after state. What does the file look like before
  the upload, and what does it look like before the download.
  \item Depending on scenario, we might have multiple components on the page,
  and therefore need to make sure, that the state of one, does not affect the
  state of the other.
  \item State is contained within a single component, albeit there might be a
  number of different components on the same page. It would seem state is
  superfluous in this scenario.
  \item Following dumb/smart component architecture, in order to keep
  application dry, we are going to need to inroduce our state from some outside
  source, using event emitters.
\end{enumerate}

The scenario that commonly applies to file upload can happen in many other
situations as well. While @ngrx/store is something which is a good idea for the
majority of any enterprise application, it is not neccesarily the right choice
in this scenario.

\subsection{Identifying Bloat of @ngrx/store}
@ngrx/store bloat is real. To put into perspective, it requires an action, a
reducer, a facade, in better architectured solutions, ngrx/entity, and
selectors. In addition, state isn't naturally re-usable, as it is an object.
Lastly, and most definitely, not least, special nomenclature must be put in
place to make it, so state can be re-used in the future.

\subsection{Architectural Danger of Using a Service}
Naturally using a service in this scenario makes the most sense. Services can
have a direct 1:1 relationship for as what they need to do. In addition, it can
help circumvent circular dependencies in numerous scenarios, by keeping heavy
logic from the store. However, services by default break away from the cookie
cutter api's brought to you by the @ngrx life cycle. It is important to
understand that if services are created, that one needs to add proper due
dilligence to make sure services are properly used.
\begin{enumerate}
  \item Documentation for each method.
  \item Functions kept small.
  \item Readme.md in root of service lib, specifying methods used.
  \item Heavy Unit Testing
\end{enumerate}

That would be it. Ideally these services are created sparingly, but they have
their advantages, wherein @ngrx/store is obvious bloat.

\mybox{
Many times in a given project, there is the potential for scope creep. That is,
product might present the data needed in a given use case, as only being used
in a certain fashion, for the entire lifecycle of the app. As time goes on,
however, this might not be true. If it is important for the developer to
map out potential areas wherein this might not be true. If you see the potential
of the business logic to expand beyond what you are working on, take that into
consideration. If not, then seriously consider using a service.
}
