\maketitle{}
\section{ Introduction to @ngrx/store }

As discussed in the chapter on the History of State Management, there has
been quite a series of progression with regards to state management. Redux, is
the mature concept of state management including actions, reducers, and a single
application store. \footnote{This is a footnote for more information on state management}.
Angular's @ngrx/store, which is not front and center, is where redux meets Rxjs.
Rxjs is the Javascript library for using observables
\footnote{More on Observables can be read here}.

\subsection{What Makes @ngrx/store Different than Redux?}
When considering this question, it is more important to consider what is
reactive programming. Reactive programming in particular introduces two concepts
\footnote{http://www-sop.inria.fr/members/Gerard.Berry/Papers/Berry-IFIP-89.pdf}:

\begin{enumerate}
  \item Asynchronous \footnote{Meaning one event fires after the previous one is
  complete, unlike synchronous which means they all fire at the same time, and
  might complete out of order.}
  \item Deterministic \footnote{Always produces the same results. As a side
  effect of this, code becomes very much so cookie cutter, which is great in
  an enterprise setting, as it allows for greater re-use.}
\end{enumerate}

\subsubsection{Asynchronous}
With regards to asynchronous, observables are not neccesarily reactive in the
strictest sense. This is because the client is working separate from the server.
Events with observables are most definitely reactive, and help, but many
applications are data heavy, and the immediate value of observables are cut
short. In addition, actual UI events from a browser perspective are put in a
call stack, and are asynchronous by nature. What does help, is that baked into
the framework is effects. Which does allow the UI to be asynchronous, but it's
not like it's anything crazy. This is something which could easily be done with
promises. However, @ngrx/store does tie it nicely into the store as a whole,
allowing client state management, without going into detail.

\subsubsection{Deterministic}
With regards to determinstic, this is
In addition, with proper UI component architecture, many components have
smart and dumb components, which

This is really the beauty of @ngrx/store, is that it offers a end to end
solution to for state management. In particular, in the form of effects, and
observables.
