\chapter{ Primer - Actions }
An action is a function which contains two very important pieces of information:
\begin{enumerate}
  \item What the name(type) of the action is. \footnote{Why this is important we
  will get to soon}
  \item The payload of the action. Which is a single object, containing all the data passed into the store.
\end{enumerate}

\section{An example of an Action in an Angular setting}
An Action is pretty generic across different frameworks.  However, within an Angular setting it means that we are using @ngrx/store for controlling state across our app and Typescript. An action will look like the following:
\begin{lstlisting}
export class LoadCodeBox extends Action {
  readonly type = CodeBoxTypes.LoadCode;

  constructor(public payload: {id: string}) { }
}

export class CodeBoxLoaded extends Action {
  readonly type = CodeBoxTypes.LoadCode;

  constructor(public payload: CodeBox) { }
}
\end{lstlisting}

This is an example representation of your classic action. It contains the type of action. So that in you reducer, or effect, we can trigger reduce(combine) data passed in, with data already present.

\mybox{In an Angular/Typescript setting, you will commonly find a general export type, for the entire app:

\lstinline{export type Actions = LoadCodeBox | CodeBoxLoaded;}

This is usually used within the reducer, and is called a union interface type. It allows us to combine the type for numerous actions within a single type. We can then pass this as a type to a reducer, and make sure that we do not introduce any action beyond that for the particular feature state. It's a great way to make the develop think twice, if they introduce an action outside of the feature state into the app.}

\section{An example of using an Action in an Angular setting}
Generally, an action will only be used in a variety of situations such as an effect, facade, or guard. As a simple example, let's use it in a facade.

\begin{lstlisting}
  loadCodeBox(id) {
    new LoadCodeBox({id})
  }
\end{lstlisting}

Here we are calling the class by using new. It will call the action whenever the facade is called.

This would be as simple as a primer can get for actions. It might seem like there are more questions that came up as a result.
