\maketitle{}
\section{ Versioning }

\subsection { Git }
It goes without saying that you should be using Git. Unless you have an
incredibly huge diffing tree in your repo, which is most of us, then you should
be using Git.

\subsection { Integration with JIRA }
In any JIRA ticket, if one has the proper webhooks setup with Github, or if one
is using BitBucket, then it will automatically hook up the commit into the
ticket. All that is neccesary, is for the the commit message to include the
ticket name. \marginpar{Screenshot for example should go here}.

\subsection { Analyzing a Git Branch }
In any git environment, the name of the git branch is important for the
following reasons:

\begin{enumerate}
  \item It can inform the developer about the type of branch
    \begin{enumerate}
      \item feature
      \item hotfix
      \item bugfix
      \item refactor
    \end{enumerate}
  \item It can inform the developer of ticket being worked on
  \item It can inform the developer of abstract of ticket.
\end{enumerate}

In addition, as we have mentioned above, it will be particularly advantageous to
having the branch name, when it comes to integrating with JIRA.

\subsection { Branching Name Convention }
Let's imagine our project is called PIXE. We have a ticket called PIXE-113,
which is responsible for adding a pixel color picker to our Pixel Illustrator
app. We would create our branch as following:

\begin{verbatim}
  feature/PIXE-113-details-and-actions
\end{verbatim}

\begin{itemize}
  \item feature is name of issue type all lowercase followed by forward slash
  \item PIXE-113 is name of ticket in all caps, followed by dash
  \item details-and-actions is abstract of ticket
\end{itemize} \marginpar{Todo: Create a graphic for this one}

\subsection { Git Client }
When it comes to using an IDE, I strongly believe that every team member should
have the freedom to use whatever they want. It is very important, in general,
that all team members feel free to use whatever they want. In this same vein
they should feel comfortable in using a client if they would like. I personally
prefer using the terminal.

\subsection { Squash and Merge }
Github, is our preferred client. It gives the option to squash and merge a
particular commit. Squashing your commits should be your preferred way of doing
commits. It allows for a clean git history.
