
\chapter{ Icons }

I would like to dedicate a quick chapter to icons, simply because I have never
come across an application that has not used icons. In addition, every app has
to make the decision, what icons they are going to use. It's interesting,
because I had less of a hesitation to write this chapter, than I did for
Material Design. With regards to icons, the choice is really ubiqitious at this
point. If you are going to use icons, it should be Font Awesome!

\section{ Font Awesome }
In short, font-awesome is the largest icon library currently available, and the
pro version is relatively cheap. In addition, there are many particulars with
icons that they solve, making sure that they look good on different devices. So,
in short I would like to reccomend font-awesome. It is the best architectural
decision you can make when it comes to fonts. Of course, unless your team has
the need to use their own icons. However, before proceeding to do so, let's
discuss some of the benefits of using Font Awesome:
\begin{enumerate}
  \item Pixel Perfect, Consistent Look.
  \item 5,000 icons and growing.
  \item Ability to play with Size on Web.
  \item Accesibility Minded
  \item Desktop Friendly.
  \item Tried and Tested, by the whole community.
  \item Multiple ways to use. CDN, Download yourself, install via NPM.
\end{enumerate}

Font Awesome truly is ubiqitious on the web. In the past 10 years that I have
been using it, it is the only consistent tool that has been used across
companies.
